Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-17 paper.tex
example

% For figures
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{color}

@@

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
define a signature $s \in p$ from a publication as a unique piece of
information identifying one of the authors of $p$ (e.g., the author name, his
affiliation, along with any other metadata that can be derived from $p$). Let us
denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
signatures that can be extracted from all publications in ${\cal P}$. In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual. Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge of pairs $(a, s) \in
{\cal A} \times {\cal S}$, each indicating that signature $s$ is known with high confidence
to belong to individual $a$.

@@

\glnote{By Mateusz}
\msnote{If the matching is not described in this paper, change appearances of "four elements"}

Having the algorithm split into four elements, we implemented each of them separately.
Learning a similarity function and semi-supervised clustering steps required sophisticated
machine learning algorithms which implementations transcended the scope of this project.
Thus, we used ready-to-go \textit{Scikit-learn} library \citep{scikit-learn} and
semi-supervised clustering from \textit{SciPy} \citep{scipy}. In order to keep the code
maintainable and abstract, we followed practices introduces by \textit{Scikit-learn API}
\citep{scikit-learn-API}.

@@

\FloatBarrier
\begin{table}[H]
\caption{Time performance (2 GHz per CPU core, 32GB RAM)}
\centering
\begin{tabular}{|l|l|}
  \hline
  \textbf{algorithm} & \textbf{time}\\
  \hline
  blocking 1200000 signatures & dfsf \\
  \hline
  learning similarity function on 1000 pairs on reduced set of features & w1k2\\
  \hline
  learning similarity function on 1000000 pairs on reduced set of features & w2k2 \\
  \hline
  learning similarity function on 1000000 pairs on full set of features & sdfsdf \\
  \hline
  clustering 1200000 signatures on reduced set of features using 16 cores & asdsda \\
  \hline
  clustering 1200000 signatures on reduced set of features using 1 cores & aasdfs \\
  \hline
  clustering 1200000 signatures on full set of features using 16 cores & ssesdf \\
  \hline
  matching clusters from 1200000 signatures with the old onews & asdsd \\
  \hline
\end{tabular}
\end{table}

>>>>

% For figures
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{color}
\usepackage{amsmath}

@@

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
define a signature $s \in p$ from a publication as a unique piece of
information identifying one of the authors of $p$ (e.g., the author name, his
affiliation, along with any other metadata that can be derived from $p$, as illustrated in Figure~\ref{fig:signature}). Let us
denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
signatures that can be extracted from all publications in ${\cal P}$ and
by $S=|{\cal S}|$ the total number of signatures.

\begin{figure}
\label{fig:signature}
\begin{tabular}{ l l l }
  $s:$ & Title & Lorem ipsum dolor sit amet, consectetur adipiscing elit \\
  & Author & Doe, John \\
  & Affiliation & University of Foo \\
  & Co-authors & Smith, John; Chen, Wang\\
  & Year & 2015\\
\end{tabular}

\caption{An example of signature $s$ for "Doe, John". A \textit{signature} is
defined as unique piece of information identifying an author on a publication,
along with any other metadata that can be derived from it, such as publication
title, co-authors or date of publication.}
\end{figure}

In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual. Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge of pairs $(a, s) \in
{\cal A} \times {\cal S}$, each indicating that signature $s$ is known with high confidence
to belong to individual $a$.

@@

Having the algorithm split into three elements, we implemented each of them separately.
Learning a similarity function and semi-supervised clustering steps required sophisticated
machine learning algorithms which implementations transcended the scope of this project.
Thus, we used ready-to-go \textit{Scikit-learn} library \citep{scikit-learn} and
semi-supervised clustering from \textit{SciPy} \citep{scipy}. In order to keep the code
maintainable and abstract, we followed practices introduces by \textit{Scikit-learn API}
\citep{scikit-learn-API}.

@@

\FloatBarrier
\begin{table}[H]
\caption{Time performance (2 GHz per CPU core, 32GB RAM)}
\centering
\begin{tabular}{|l|l|}
  \hline
  \textbf{algorithm} & \textbf{time}\\
  \hline
  blocking 1200000 signatures & dfsf \\
  \hline
  learning similarity function on 1000 pairs on reduced set of features & w1k2\\
  \hline
  learning similarity function on 1000000 pairs on reduced set of features & w2k2 \\
  \hline
  learning similarity function on 1000000 pairs on full set of features & sdfsdf \\
  \hline
  clustering 1200000 signatures on reduced set of features using 16 cores & asdsda \\
  \hline
  clustering 1200000 signatures on reduced set of features using 1 cores & aasdfs \\
  \hline
  clustering 1200000 signatures on full set of features using 16 cores & ssesdf \\
  \hline
\end{tabular}
\end{table}
